---
title: "Untitled"
output: html_document
date: "2024-09-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# How to describe your code problems and get help online.

The key to receiving help from someone is for them to rapidly grasp your
problem. Thus, you should be as precise as possible when describing your problem
and help others to pinpoint where the issue might be. Try to...

- Use the correct words to describe your problem. Otherwise you might get an
  answer pointing to the misuse of your words rather than answering your
  question.

- Generalize what you are trying to do, so people outside your field can
  understand the question.

- Reduce what does not work to a simple *reproducible example*. For instance,
  instead of using your real data set, create a small generic one. For more
  information on how to write a reproducible example see [this article from
  the reprex
  package](https://reprex.tidyverse.org/articles/reprex-dos-and-donts.html).
  Learning how to use the [reprex](https://cran.r-project.org/package=reprex)
  package is also very helpful for this.

- Include the output of `sessionInfo()` in your question. It provides
  information about your platform, the versions of R and the packages that you
  are using. As an example, here you can see the versions of R and all the
  packages that we are using to run the code in this lesson:



```{r, results="show", purl=FALSE}
sessionInfo()
```

#### How to ask good programming questions?

- The rOpenSci community call "How to ask questions so they get answered",
  ([rOpenSci site](https://ropensci.org/commcalls/2017-03-07/) and [video
  recording](https://vimeo.com/208749032)) includes a presentation of the
  reprex package and of its philosophy.
- [blog.Revolutionanalytics.com](https://blog.revolutionanalytics.com/2014/01/how-to-ask-for-r-help.html)
  and [this blog post by Jon Skeet](https://codeblog.jonskeet.uk/2010/08/29/writing-the-perfect-question/)
  have comprehensive advice on how to ask programming questions.